### 2020-08-03 paper/sex_selection_spacing-ver4.tex
Edit Data section

I focus on the three birth intervals starting from the first birth and ending with the 
fourth birth.
I exclude the interval from marriage to the first birth because many are imputed and the
higher-order intervals because few women had five or more births, especially among the 
better-educated.

@@

In addition to a large number of women surveyed and the long period covered, a significant 
benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
spacing between births and probe for ``missed'' births.
For India, the main concern is underreporting of deceased children, especially a systematic 
recall error where respondents' likelihood of reporting the birth of a deceased child depends 
on the sex of that child.
Unreported deceased children inflate the birth intervals and, with declining mortality, 
make changes over time appear too small.
I, therefore, provide a detailed analysis of systematic recall error in the Online Appendix.
Recall error depends heavily on how long ago a woman was married, and I, consequently, 
drop women married 22 years or more.%
\footnote{
Recall error is likely behind the designation of the first two rounds of NFHS as ``moderate 
quality'' in an analysis of the quality of birth histories in DHS surveys and its impact 
on fertility estimates \citep{Schoumaker2014}.
}

To ensure that there are enough births for the method to work, I censor each spell at 96 
months (eight years) after a woman can first give birth, which is equivalent to 105 months 
after the birth of the prior child.
Less than one percent of observed births occur after the cut-off.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

@@

I divide the explanatory variables into two groups.
The first group consists of characteristics that the prior literature finds affect 
the spacing choice and the use of sex selection:
mother's education, sex composition of previous children, and area of residence.%
\footnote{
With sex selection, the composition of prior children is, in principle, endogenous.
It is beyond the scope of this paper to develop a method for dealing with this issue.
}
The second group of variables consists of those expected to have an approximately 
proportional effect on the hazard.
These include the mother's age when the spell begins, the household's
land ownership, and whether it belongs to a scheduled tribe or caste.
Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present descriptive statistics.

I estimate a separate model for each birth interval, education group, and period 
combination to minimize any potential bias from including proportional variables.
I capture sex composition with dummy variables for the
possible combinations, ignoring the ordering of births.
Area of residence is a dummy variable for living in an urban area.

>>>>

I focus on the three spells starting from the first birth and ending with the 
fourth birth.
I exclude the interval from marriage to the first birth because many are imputed and the
higher-order intervals because few women had five or more births, especially among the 
better-educated.

@@

In addition to a large number of women surveyed and the long period covered, a significant 
benefit of the NFHS over other surveys is that enumerators pay careful attention to the 
spacing between births and probe for ``missed'' births.
For India, the main concern is underreporting of deceased children, especially a systematic 
recall error where respondents' likelihood of reporting the birth of a deceased child depends 
on the sex of that child.
Unreported deceased children inflate the birth intervals and, with declining mortality, 
make changes over time appear too small.
In the Online Appendix, I provide a detailed analysis of systematic recall error, which 
shows that recall error depends heavily on how long ago a woman was married. 
I, consequently, drop women married 22 years or more.%
\footnote{
Recall error is likely behind the designation of the first two rounds of NFHS as ``moderate 
quality'' in an analysis of the quality of birth histories in DHS surveys and its impact 
on fertility estimates \citep{Schoumaker2014}.
}

To ensure that there are enough births for the method to work, I censor spells at 96 
months (eight years) after a woman can first give birth, equivalent to 105 months 
after the birth of the prior child.
Less than one percent of observed births occur after the cut-off.
The final sample consists of 
\input{../tables/num_women.tex}
% [number] women, with [number] parity one through four births.

@@

I divide the explanatory variables into two groups, non-proportional and proportional. 
The first group consists of characteristics that the prior literature finds affect the 
spacing choice and the use of sex selection: mother’s education, sex composition of 
previous children, and area of residence. 
To minimize any potential bias from including proportional variables, I estimate a 
separate model for each birth interval, education group, and period combination, rather 
than including education as a variable. 
I capture sex composition with dummy variables for the possible combinations, ignoring 
the ordering of births.%
\footnote{
With sex selection, the composition of prior children is, in principle, endogenous. 
It is beyond the scope of this paper to develop a method for dealing with this issue. 
}
Area of residence is a dummy variable for living in an urban area.

The second group of variables consists of those expected to have an approximately 
proportional effect on the hazard.
These include the mother's age when the spell begins, the household's
land ownership, and whether it belongs to a scheduled tribe or caste.
Appendix Tables \ref{tab:des_stat1} and \ref{tab:des_stat2} present descriptive statistics.
